method

### 2022-02-17 06_Paper/ER-ED/method.Rmd
corrected ANOVAs

# figure
FigSubjArousalViewPilot=ggplot2::ggplot(Ratings_view, aes(x = block, y = arousal))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("view_neu", "view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Arousal Rating")

@@

Ratings_reg <- data_ER %>%
  subset(data_ER$block != "view_neu" & data_ER$block != "choice")
Ratings_reg$block <- as.factor(Ratings_reg$block)

@@

SubjArousalReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "view_neg"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "distraction"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "view_neg"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "distancing"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "view_neg"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "suppression"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "distraction"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "distancing"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "distraction"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "suppression"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "distancing"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "suppression"],
                                                                         progress = FALSE, paired = TRUE))$bf)

>>>>

# figure
FigSubjArousalViewPilot=ggplot2::ggplot(Ratings_view, aes(x = block, y = arousal))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("1_view_neu", "2_view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Arousal Rating")

@@

Ratings_reg <- data_ER %>%
  subset(data_ER$block != "1_view_neu" & data_ER$block != "6_choice")
Ratings_reg$block <- as.factor(Ratings_reg$block)

@@

SubjArousalReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "2_view_neg"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "3_distraction"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "2_view_neg"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "4_distancing"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "2_view_neg"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "5_suppression"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "3_distraction"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "4_distancing"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "3_distraction"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "5_suppression"],
                                                                         progress = FALSE, paired = TRUE))$bf,
                             BayesFactor::extractBF(BayesFactor::ttestBF(x = Ratings_reg$arousal[Ratings_reg$block == "4_distancing"],
                                                                         y = Ratings_reg$arousal[Ratings_reg$block == "5_suppression"],
                                                                         progress = FALSE, paired = TRUE))$bf)
